### 2022-04-02 manuscript.tex
april2 [ci skip]
This build is based on
https://github.com/scherzerthesis/thesis/commit/0fa019fc01a326428db51f405b30eb6701837e33.

This commit was created by the following CI build and job:
https://github.com/scherzerthesis/thesis/commit/0fa019fc01a326428db51f405b30eb6701837e33/checks
https://github.com/scherzerthesis/thesis/actions/runs/2082282600

This manuscript
(\href{https://scherzerthesis.github.io/thesis/v/0f21057cb2e3dcbcb14167218e80695a4c2cef5c/}{permalink})
was automatically generated
from \href{https://github.com/scherzerthesis/thesis/tree/0f21057cb2e3dcbcb14167218e80695a4c2cef5c}{scherzerthesis/thesis@0f21057}
on April 1, 2022.

@@

\begin{figure}
\hypertarget{fig:04}{%
\centering
\includegraphics[width=1\textwidth,height=\textheight]{images/pdgfr2.png}
\caption{\textbf{This is the title of Figure} this is the text.**}\label{fig:04}
}
\end{figure}

\begin{figure}
\hypertarget{fig:11}{%
\centering
\includegraphics[width=0.1\textwidth,height=\textheight]{images/p53_1.png}
\caption{\textbf{Differential BRAF\textsuperscript{V600E} lung tumorigenesis imparted by p53-Hotspot mutants.} \textbf{(A)} Genetically-engineered alleles of \emph{Braf\textsuperscript{v600E}} and \textsuperscript{Trp53} before and after Cre-Recombinase. \textbf{(B)} Tumor burden and \emph{(C)}** Tumor size of BRAF(V600E) plus Trp53-wildtype, null, or mutant alleles 14 weeks post Cre-mediated recombination. \emph{(D)} Representative H\&E images 14 weeks after Cre-recombination. \textbf{(E)} Survival of mice with Heterozygous \emph{Trp53} mutant alleles. \textbf{(F)} Survival of mice with homozygous \emph{Trp53} alleles.}\label{fig:11}
}
\end{figure}

\begin{figure}
\hypertarget{fig:12}{%
\centering
\includegraphics[width=1\textwidth,height=\textheight]{images/p53_2.png}
\caption{\textbf{Missense mutant-p53 alters lung adenocarcinoma differentiation status and accumulation of mutant-p53 correlates with p19 ARF expression.} \textbf{(A)} Panel representative IHC sections stained with SPC,NKX2-1, p53 and HMGA2. \textbf{(B)} H-score of individual tumors. \textbf{(C)} Association between mutant-p53 R172H accumulation and increased malignancy and dedifferentiation. \textbf{(D)} serial section of P53-HI and pERK1/2-HI tumors compared to adjacent low. \textbf{(E)} Colocalization of p19/ARF and p53 in p53-mutant. tumors}\label{fig:12}
}
\end{figure}

\begin{figure}
\hypertarget{fig:13}{%
\centering
\includegraphics[width=1\textwidth,height=\textheight]{images/p53_3.png}
\caption{\textbf{Mutant-p53 cell lines are refractory to BRAFi+MEKi.} \textbf{(A)} Response of GEMMs to BRAFi+MEKi chow after four weeks \textbf{(B)} in vitro dose response to BRAFi single agent. \textbf{(C)} in vitro timecourse with dabrafenib (1000nm) plus trametinib (100nM). \textbf{(D)} Accumulation of dead cells in dabrafenib plus trametinib measured by CytotoxRed accumulation. \textbf{(E)} Immunoblotting of phospho-ERK1/2 in response to dabrafenib plus trametinib. \textbf{(F)} Ectopic expression of p53\textsuperscript{R17H} in human HCC364 cells. \textbf{(E)} Response of p53\textsuperscript{R175H} cells to dabrafenib plus trametinib.}\label{fig:13}
}
\end{figure}

\begin{figure}
\hypertarget{fig:14}{%
\centering
\includegraphics{images/p53_4.png}
\caption{\textbf{Mutant-p53 expression cells have distinct transcriptome compared to p53-null cells.} \textbf{(A)} Volcano plot of differentially-expressed genes. \textbf{(B)} Upregulated pathways using GSEA with Hallmark gene sets.}\label{fig:14}
}
\end{figure}

\begin{figure}
\hypertarget{fig:04}{%
\centering
\includegraphics[width=1\textwidth,height=\textheight]{images/p53_5.png}
\caption{\textbf{This is the title of Figure} this is the text.**}\label{fig:04}
}
\end{figure}

\begin{figure}
\hypertarget{fig:04}{%
\centering
\includegraphics[width=1\textwidth,height=\textheight]{images/p536.png}
\caption{\textbf{This is the title of Figure} this is the text.**}\label{fig:04}
}
\end{figure}

\begin{figure}
\hypertarget{fig:04}{%
\centering
\includegraphics[width=1\textwidth,height=\textheight]{images/p537.png}
\caption{\textbf{This is the title of Figure} this is the text.**}\label{fig:04}
}
\end{figure}

\begin{figure}
\hypertarget{fig:04}{%
\centering
\includegraphics[width=1\textwidth,height=\textheight]{images/p538.png}
\caption{\textbf{This is the title of Figure} this is the text.**}\label{fig:04}
}
\end{figure}

\begin{figure}
\hypertarget{fig:04}{%
\centering
\includegraphics[width=1\textwidth,height=\textheight]{images/p539.png}
\caption{\textbf{This is the title of Figure} this is the text.**}\label{fig:04}
}
\end{figure}

\begin{figure}
\hypertarget{fig:04}{%
\centering
\includegraphics[width=1\textwidth,height=\textheight]{images/p5310.png}
\caption{\textbf{This is the title of Figure} this is the text.**}\label{fig:04}
}
\end{figure}

\begin{figure}
\hypertarget{fig:04}{%
\centering
\includegraphics[width=1\textwidth,height=\textheight]{images/p5311.png}
\caption{\textbf{This is the title of Figure} this is the text.**}\label{fig:04}
}
\end{figure}

\begin{figure}
\hypertarget{fig:04}{%
\centering
\includegraphics[width=1\textwidth,height=\textheight]{images/pdgfr_1.png}
\caption{\textbf{This is the title of Figure} this is the text.**}\label{fig:04}
}
\end{figure}

\begin{figure}
\hypertarget{fig:04}{%
\centering
\includegraphics[width=1\textwidth,height=\textheight]{images/pdgfr_2.png}
\caption{\textbf{This is the title of Figure} this is the text.**}\label{fig:04}
}
\end{figure}

@@

@@

\begin{figure}
\hypertarget{fig:04}{%
\centering
\includegraphics[width=1\textwidth,height=\textheight]{images/scrna_1.png}
\caption{All lung cells collected from different genotypes.}\label{fig:04}
}
\end{figure}

@@

\hypertarget{chapter-six-methods}{%
\subsection{Chapter Six: methods}\label{chapter-six-methods}}

@@

\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1624}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1709}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2308}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1368}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2991}}@{}}
\caption{\textbf{Critical reagents} \label{tbl:reagents}}\tabularnewline
\toprule
\begin{minipage}[b]{\linewidth}\raggedright
\textbf{Reagents List}
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Reagent Type
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Name
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Source
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Catalog number
\end{minipage} \\
\midrule
\endfirsthead
\toprule
\begin{minipage}[b]{\linewidth}\raggedright
\textbf{Reagents List}
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Reagent Type
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Name
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Source
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Catalog number
\end{minipage} \\
\midrule
\endhead
antibody & beta-Actin & CST & 3700T & wb: 1:10,000 \\
antibody & Phospho ERK1/2 & CST & 4370 & wb:1:2000, IHC:1:1000 \\
antibody & ERK1/2 & CST & 4696 & wb: 1:2000 \\
antibody & P53 & Leica & cm-5 & wb: 1:2000, IHC: 1:1000, IF:1:250 \\
antibody & NKX2-1 & Abcam & ab76013 & IHC: 1:1000 \\
antibody & Pro-SPC & Millipore & Cat\# AB3786 & IHC: 1:2000 \\
antibody & HMGA2 & CST & 8179S & IHC 1:2000 \\
antibody & p19/ARF & Chuck Sherr & (Bertwistle et al., 2004) & \\
Cell Line & 293T & ATCC & CRL-3216 & \\
Cell Line & HCC-364 & Bivona lab & (Lin et al., 2014) & \\
Recombinant DNA & Pmd2.5 & Addgene & \#12259 & \\
Recombinant DNA & pspax2 & Addgene & \#12260 & \\
Recombinant DNA & P53-R175H & Addgene & \#22936 & \\
Chemical Compound & dabrafenib & Selleck & S2807 & \\
Chemical Compound & PLX4720 & Plexxikon/ Research Diets & & \\
Chemical Compound & trametinib & Selleck & S2673 & \\
Other & Collagenase type 1 & Thermo Fischer Scientific & 17100017 & \\
Other & Dispase & Corning & 354235 & \\
other & Elastase & Worthington Biochem & LS006365 & \\
other & ad5spc-Cre & university of Iowa & VVC-Berns1168 & \\
\bottomrule
\end{longtable}

@@

\hypertarget{refs}{}
\begin{CSLReferences}{0}{0}
\leavevmode\vadjust pre{\hypertarget{ref-8Gf0ScB2}{}}%
(2014). \href{https://doi.org/10.1038/nature13385}{Comprehensive molecular profiling of lung adenocarcinoma.} Nature \emph{511}, 543--550.

\leavevmode\vadjust pre{\hypertarget{ref-179MWicwA}{}}%
(2020). \href{https://doi.org/10.1038/s41586-020-2496-1}{A single-cell transcriptomic atlas characterizes ageing tissues in the mouse.} Nature \emph{583}, 590--595.

\leavevmode\vadjust pre{\hypertarget{ref-JyurLVYi}{}}%
Abegglen, L.M., Caulin, A.F., Chan, A., Lee, K., Robinson, R., Campbell, M.S., Kiso, W.K., Schmitt, D.L., Waddell, P.J., Bhaskara, S., et al. (2015). \href{https://doi.org/10.1001/jama.2015.13134}{Potential Mechanisms for Cancer Resistance in Elephants and Comparative Cellular Response to DNA Damage in Humans.} JAMA \emph{314}, 1850--1860.

\leavevmode\vadjust pre{\hypertarget{ref-1HKPvGqty}{}}%
Adorno, M., Cordenonsi, M., Montagner, M., Dupont, S., Wong, C., Hann, B., Solari, A., Bobisse, S., Rondina, M.B., Guzzardo, V., et al. (2009). \href{https://doi.org/10.1016/j.cell.2009.01.039}{A Mutant-p53/Smad complex opposes p63 to empower TGFbeta-induced metastasis.} Cell \emph{137}, 87--98.

\leavevmode\vadjust pre{\hypertarget{ref-vsbCfYx4}{}}%
Alanis, D.M., Chang, D.R., Akiyama, H., Krasnow, M.A., and Chen, J. (2014). \href{https://doi.org/10.1038/ncomms4923}{Two nested developmental waves demarcate a compartment boundary in the mouse lung.} Nat Commun \emph{5}, 3923.

\leavevmode\vadjust pre{\hypertarget{ref-e3rkxhDE}{}}%
Alexandrov, L.B., Ju, Y.S., Haase, K., Van Loo, P., Martincorena, I., Nik-Zainal, S., Totoki, Y., Fujimoto, A., Nakagawa, H., Shibata, T., et al. (2016). \href{https://doi.org/10.1126/science.aag0299}{Mutational signatures associated with tobacco smoking in human cancer.} Science \emph{354}, 618--622.

\leavevmode\vadjust pre{\hypertarget{ref-6j21xB75}{}}%
Arteaga, C.L., and Engelman, J.A. (2014). \href{https://doi.org/10.1016/j.ccr.2014.02.025}{ERBB receptors: from oncogene discovery to basic science to mechanism-based cancer therapeutics.} Cancer Cell \emph{25}, 282--303.

@@

\leavevmode\vadjust pre{\hypertarget{ref-18dmdoj17}{}}%
Bertwistle, D., Zindy, F., Sherr, C.J., and Roussel, M.F. (2004). \href{https://doi.org/10.1089/hyb.2004.23.293}{Monoclonal antibodies to the mouse p19(Arf) tumor suppressor protein.} Hybrid Hybridomics \emph{23}, 293--300.

\leavevmode\vadjust pre{\hypertarget{ref-1AV7mz5Fc}{}}%
Bhattacharya, S., and Workman, J.L. (2020). \href{https://doi.org/10.1186/s13072-020-00362-8}{Regulation of SETD2 stability is important for the fidelity of H3K36me3 deposition.} Epigenetics Chromatin \emph{13}, 40.

\leavevmode\vadjust pre{\hypertarget{ref-ju5z9qDz}{}}%
Bouaoun, L., Sonkin, D., Ardin, M., Hollstein, M., Byrnes, G., Zavadil, J., and Olivier, M. (2016). \href{https://doi.org/10.1002/humu.23035}{TP53 Variations in Human Cancers: New Lessons from the IARC TP53 Database and Genomics Data.} Hum Mutat \emph{37}, 865--876.

\leavevmode\vadjust pre{\hypertarget{ref-GiCMgc6K}{}}%
Bougeard, G., Sesboüé, R., Baert-Desurmont, S., Vasseur, S., Martin, C., Tinat, J., Brugières, L., Chompret, A., de Paillerets, B.B., Stoppa-Lyonnet, D., et al. (2008). \href{https://doi.org/10.1136/jmg.2008.057570}{Molecular basis of the Li-Fraumeni syndrome: an update from the French LFS families.} J Med Genet \emph{45}, 535--538.

\leavevmode\vadjust pre{\hypertarget{ref-KlPsMirp}{}}%
Boutelle, A.M., and Attardi, L.D. (2021). \href{https://doi.org/10.1016/j.tcb.2020.12.011}{p53 and Tumor Suppression: It Takes a Network.} Trends Cell Biol \emph{31}, 298--310.

\leavevmode\vadjust pre{\hypertarget{ref-Ph0Z7rTW}{}}%
Cerami, E., Gao, J., Dogrusoz, U., Gross, B.E., Sumer, S.O., Aksoy, B.A., Jacobsen, A., Byrne, C.J., Heuer, M.L., Larsson, E., et al. (2012). \href{https://doi.org/10.1158/2159-8290.cd-12-0095}{The cBio cancer genomics portal: an open platform for exploring multidimensional cancer genomics data.} Cancer Discov \emph{2}, 401--404.

\leavevmode\vadjust pre{\hypertarget{ref-1EwtuJJw6}{}}%
Chiou, S.-H., Winters, I.P., Wang, J., Naranjo, S., Dudgeon, C., Tamburini, F.B., Brady, J.J., Yang, D., Grüner, B.M., Chuang, C.-H., et al. (2015). \href{https://doi.org/10.1101/gad.264861.115}{Pancreatic cancer modeling using retrograde viral vector delivery and in vivo CRISPR/Cas9-mediated somatic genome editing.} Genes Dev \emph{29}, 1576--1585.

\leavevmode\vadjust pre{\hypertarget{ref-G5wVcRrJ}{}}%
Christophorou, M.A., Ringshausen, I., Finch, A.J., Swigart, L.B., and Evan, G.I. (2006). \href{https://doi.org/10.1038/nature05077}{The pathological response to DNA damage does not contribute to p53-mediated tumour suppression.} Nature \emph{443}, 214--217.

>>>>

This manuscript
(\href{https://scherzerthesis.github.io/thesis/v/0fa019fc01a326428db51f405b30eb6701837e33/}{permalink})
was automatically generated
from \href{https://github.com/scherzerthesis/thesis/tree/0fa019fc01a326428db51f405b30eb6701837e33}{scherzerthesis/thesis@0fa019f}
on April 2, 2022.

@@

\begin{figure}
\hypertarget{fig:04}{%
\centering
\includegraphics[width=1\textwidth,height=\textheight]{images/p53_1.png}
\caption{Cre-mediated wildtype-to-mutant alleles used in study. (A) Priot to Cre-mediated recombination, normal \emph{Braf} and \emph{Trp53} are expressed from their endogenous loci. (B) After Cre-mediated recombination, the indicated mutant proteins are expressed, in addition to a TdTomato fluorescent protein to mark expression of BRAF\textsuperscript{V600E}.}\label{fig:04}
}
\end{figure}

\begin{figure}
\hypertarget{fig:04}{%
\centering
\includegraphics[width=1\textwidth,height=\textheight]{images/p53_2.png}
\caption{Mutant-p53 alleles differentially alter BRAF\textsuperscript{V600E} driven lung tumorigenesis. (A) Tumor burden analysis 14-weeks post Cre-recombinase. (B) Tumor size 14 weeks post Cre-Recombinase. (C) Representative histological images 14 weeks post Cre-Recombinase. *** = \emph{p-value\textless.01}}\label{fig:04}
}
\end{figure}

\begin{figure}
\hypertarget{fig:04}{%
\centering
\includegraphics[width=1\textwidth,height=\textheight]{images/p53_3.png}
\caption{Mutant-p53 alleles differentially affect the survival of mice due to progressive lung adenocarcinoma. (A) Kaplan-Meier plot of \emph{Braf\textsuperscript{CAT/+}} mice with p53-mutant alleles. (B) Kaplan-Meier plot of \emph{Braf\textsuperscript{CAT/+}} mice with homozygous p53-mutant alleles.* = \emph{p-value\textless.05}}\label{fig:04}
}
\end{figure}

\begin{figure}
\hypertarget{fig:04}{%
\centering
\includegraphics[width=1\textwidth,height=\textheight]{images/p53_4.png}
\caption{Missense mutant-p53 alters lung adenocarcinoma differentiation status. (A)Representative IHC images of tumors stained with antibodies targeting p53, NKX2-1, SPC, and HMGA2. (B) Quantification of immunostaing in (A) based on H-Score. *** = \emph{p-value\textless.01} ; **** = \emph{p-value\textless.001}.}\label{fig:04}
}
\end{figure}

\begin{figure}
\hypertarget{fig:04}{%
\centering
\includegraphics[width=1\textwidth,height=\textheight]{images/p53_5.png}
\caption{p53-accumulation occurs in high grade tumors and correlates with p19/ARF expression. (A) Representative images of mutant-p53 accumulation in high grade tumors. the tumor area encased by the dashed line exhibit nuclear atypia and enlarged nuclei.(B) Mutant-p53 immunostaining correlates with phospho-ERK1/2 accumulation. (C) p53 immunostaining correlates with loss of SPC expression. (D) mutant-p53 is co-expressed with p19/ARF in p53-mutant tumors.}\label{fig:04}
}
\end{figure}

\begin{figure}
\hypertarget{fig:04}{%
\centering
\includegraphics[width=1\textwidth,height=\textheight]{images/p536.png}
\caption{Mouse tumors and cell lines that expression P53-R172H and p53-R245W are refractory to MAPK blockade. (A) Tumor burden analysis of GEMMs treated with MAPKi chow for four weeks. (B) \emph{n vitro} dose response to dabrafenib for 48 hours. (C) Western blots of timecourse of cell lines treated with dabrafenib plus trametinib.}\label{fig:04}
}
\end{figure}

\begin{figure}
\hypertarget{fig:04}{%
\centering
\includegraphics[width=1\textwidth,height=\textheight]{images/p537.png}
\caption{p53-R172H and p53-R245W cell lines are insensitive to MAPKi-induced cell death (A-C) Incucyte analysis of cell lines treated with the combination of dabrafinib plus trametinib for 96 hours. (D) Accumulation of dead cells in response to dabrafinib plus trametinib. Dead cells were quantified by CytoTox Red Dye.}\label{fig:04}
}
\end{figure}

\begin{figure}
\hypertarget{fig:04}{%
\centering
\includegraphics[width=1\textwidth,height=\textheight]{images/p538.png}
\caption{HCC-364 cells that express p53-R175H are refractory to MAPKi. (A) Western blot showing successful ectopic expression of p53-R175H. (B) Incucyte analysis of HCC364 parental and HCC364+p53-R175H in response to dabrafenib plus trametenib.}\label{fig:04}
}
\end{figure}

\begin{figure}
\hypertarget{fig:04}{%
\centering
\includegraphics[width=1\textwidth,height=\textheight]{images/p539.png}
\caption{P53-R172H and p53-R245W cell lines have altered transcriptome compared to p53-null cell lines. (A) Volcano plot showing up- and down- regulated genes compared to p53-null cells. (B) Pathway analysis of Differentially expressed genes of p53-R172H and p53-R245W cell lines compared to p53-null cell lines.}\label{fig:04}
}
\end{figure}

\begin{figure}
\hypertarget{fig:04}{%
\centering
\includegraphics[width=1\textwidth,height=\textheight]{images/p5310.png}
\caption{Comparison of differentially-expressed genes between p53-R172H and p53-R245W cell lines. (A) Volcano plot of differntially expressed gene between p53-R172H and p53-R245W tumor-derived cell lines. (B) Pathway analysis of differentially expressed genes between p53-R172H and p53-R245W tumor-derived cell lines.}\label{fig:04}
}
\end{figure}

\begin{figure}
\hypertarget{fig:04}{%
\centering
\includegraphics[width=1\textwidth,height=\textheight]{images/p5311.png}
\caption{PDGFRB is upregulated and expressed in mutant-p53 tumors and cell lines. (A) Log-normalized counts of \emph{Pdgfrb} RNA reads from p53-mutant cell lines. (B) Western blot analysis of basal and PDGF-BB stimulated cells. (C) IHC of PDGFRB in p53-mutant GEMM tumors.}\label{fig:04}
}
\end{figure}

\begin{figure}
\hypertarget{fig:04}{%
\centering
\includegraphics[width=1\textwidth,height=\textheight]{images/p5312.png}
\caption{PDGF-stimulation or PDGF patway blockade has no effect on cell proliferation. (A) Growth response to PDGF stimulation. (B) Growth response to Imatinib treatment.}\label{fig:04}
}
\end{figure}

@@

\textbf{ScRNA Sequencing of benign and malignant BRAF\textsuperscript{V600E} mouse lung tumors}
We profiled the single-cell transcriptome of six different BRAF\textsuperscript{V600E} mouse lung tumor models including BRAF\textsuperscript{V600E} on its own, BRAF\textsuperscript{V600E} plus either mutant \emph{Pik3ca\textsuperscript{H1047R/+}}, \emph{Cdkn2a\textsuperscript{fl/fl}}, \emph{Trp53\textsuperscript{fl/fl}}, \emph{Trp53\textsuperscript{R172H/R172H}}, or \emph{Trp53\textsuperscript{R245W/R245W}}. We also treated each genotype with dabrafenib (100mg/kg) plus trametinib(2mg/kg) once daily for four days prior to tissue harvesting and 10X genomics library preperation.Importantly, we kept dabrafenib and trametinib throughout all stages of processing to prevent altered transcription in response to drug cessation. Using fluorescently-activated cell sorting (FACS), we purified tumor cells based on Td-Tomato expression 8 weeks after tumor initiation using adenoviral Spc-Cre. In sum, we were able to identify 71,110 cells that passed standard 10X genomics and Seuratbased quality control and filtering (Figure 4.1).

Although we sought to purify tumor cells based on TdTomato-positivity, we did unintentionally collect and analyze stromal cells, such as immune, mesenchymal, and endothelial cell, which are also present in the murine distal lung epithelium (Figure 4.2). Therefore, we removed these cells based on their expression of \emph{Ptprc}(immune), \emph{Pecam1} (endothelial), \emph{and Pdgfra} (mesenchymal) for downstream analysis (Figure 4.3).

Reclustering of only tumor cells(based on their expression of TdTomato and AT2 identity) revealed significant tumor cell heterogeneity(Figure 4.4). Next we sought to determine cluster specific markers using DESEQ2 analysis (Figure 4.5). strong markers of each cluster include

We next sought to determine the effect of dabrafenib plus trametinib on transcriptional heterogeneity (Figure 4.6). Clearly, there is a MAPK specific gene expression program that is decreased in most if not all clusters and genotpes (Figre 4.7).

We were also interested in genotype-specific differences. therefore, we performed DESEQ2 between vehicle-treated mice of each genotype (Figure 4.8).

@@

\begin{figure}
\hypertarget{fig:04}{%
\centering
\includegraphics[width=1\textwidth,height=\textheight]{images/scrna_1.png}
\caption{71,110 cells collected from different genotypes.}\label{fig:04}
}
\end{figure}

@@

\hypertarget{materials-and-methods}{%
\subsection{Materials and Methods}\label{materials-and-methods}}

@@

\textbf{Single Cell RNA-Seq analysis} Mice were initiated as described previusly using ad5-Spc-Cre. Four days prior to tissue harvesting, mice were either treated with corn oil control or corn oil with dabrafenib (150mg/kg) and trametenib(2mg/kg) once daily and again two hours prior to tissue harvest. single cell suspensions were made using enzymatic digestion, as previously detailed in cell line generation. Single-cell suspensions were then sorted with the BD ARIA II flow cytometer. 10X genomics library prep and sequencing was performed by HCI high throughput genomics core. Seurat objects where then created for downstream differential gene expression analysis and visualization with ggplots2.

\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1624}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1709}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2308}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1368}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2991}}@{}}
\caption{\textbf{Critical reagents} \label{tbl:reagents}}\tabularnewline
\toprule
\begin{minipage}[b]{\linewidth}\raggedright
\textbf{Reagents List}
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Reagent Type
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Name
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Source
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Catalog number
\end{minipage} \\
\midrule
\endfirsthead
\toprule
\begin{minipage}[b]{\linewidth}\raggedright
\textbf{Reagents List}
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Reagent Type
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Name
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Source
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Catalog number
\end{minipage} \\
\midrule
\endhead
antibody & beta-Actin & CST & 3700T & wb: 1:10,000 \\
antibody & Phospho ERK1/2 & CST & 4370 & wb:1:2000, IHC:1:1000 \\
antibody & ERK1/2 & CST & 4696 & wb: 1:2000 \\
antibody & P53 & Leica & cm-5 & wb: 1:2000, IHC: 1:1000, IF:1:250 \\
antibody & NKX2-1 & Abcam & ab76013 & IHC: 1:1000 \\
antibody & Pro-SPC & Millipore & Cat\# AB3786 & IHC: 1:2000 \\
antibody & HMGA2 & CST & 8179S & IHC 1:2000 \\
antibody & p19/ARF & Chuck Sherr & (Bertwistle et al., 2004) & \\
Cell Line & 293T & ATCC & CRL-3216 & \\
Cell Line & HCC-364 & Bivona lab & (Lin et al., 2014) & \\
Recombinant DNA & Pmd2.g & Addgene & \#12259 & \\
Recombinant DNA & pspax2 & Addgene & \#12260 & \\
Recombinant DNA & P53-R175H & Addgene & \#22936 & \\
Chemical Compound & dabrafenib & Selleck & S2807 & \\
Chemical Compound & PLX4720 & Plexxikon/ Research Diets & & \\
Chemical Compound & trametinib & Selleck & S2673 & \\
Other & Collagenase type 1 & Thermo Fischer Scientific & 17100017 & \\
Other & Dispase & Corning & 354235 & \\
other & Elastase & Worthington Biochem & LS006365 & \\
other & ad5spc-Cre & university of Iowa & VVC-Berns1168 & \\
\bottomrule
\end{longtable}

@@

\hypertarget{refs}{}
\begin{CSLReferences}{0}{0}
\leavevmode\vadjust pre{\hypertarget{ref-8Gf0ScB2}{}}%
(2014). Comprehensive molecular profiling of lung adenocarcinoma. Nature \emph{511}, 543--550. \url{https://doi.org/10.1038/nature13385}.

\leavevmode\vadjust pre{\hypertarget{ref-179MWicwA}{}}%
(2020). A single-cell transcriptomic atlas characterizes ageing tissues in the mouse. Nature \emph{583}, 590--595. \url{https://doi.org/10.1038/s41586-020-2496-1}.

\leavevmode\vadjust pre{\hypertarget{ref-JyurLVYi}{}}%
Abegglen, L.M., Caulin, A.F., Chan, A., Lee, K., Robinson, R., Campbell, M.S., Kiso, W.K., Schmitt, D.L., Waddell, P.J., Bhaskara, S., et al. (2015). Potential Mechanisms for Cancer Resistance in Elephants and Comparative Cellular Response to DNA Damage in Humans. JAMA \emph{314}, 1850--1860. \url{https://doi.org/10.1001/jama.2015.13134}.

\leavevmode\vadjust pre{\hypertarget{ref-1HKPvGqty}{}}%
Adorno, M., Cordenonsi, M., Montagner, M., Dupont, S., Wong, C., Hann, B., Solari, A., Bobisse, S., Rondina, M.B., Guzzardo, V., et al. (2009). A Mutant-p53/Smad complex opposes p63 to empower TGFbeta-induced metastasis. Cell \emph{137}, 87--98. \url{https://doi.org/10.1016/j.cell.2009.01.039}.

\leavevmode\vadjust pre{\hypertarget{ref-vsbCfYx4}{}}%
Alanis, D.M., Chang, D.R., Akiyama, H., Krasnow, M.A., and Chen, J. (2014). Two nested developmental waves demarcate a compartment boundary in the mouse lung. Nat Commun \emph{5}, 3923. \url{https://doi.org/10.1038/ncomms4923}.

\leavevmode\vadjust pre{\hypertarget{ref-e3rkxhDE}{}}%
Alexandrov, L.B., Ju, Y.S., Haase, K., Van Loo, P., Martincorena, I., Nik-Zainal, S., Totoki, Y., Fujimoto, A., Nakagawa, H., Shibata, T., et al. (2016). Mutational signatures associated with tobacco smoking in human cancer. Science \emph{354}, 618--622. \url{https://doi.org/10.1126/science.aag0299}.

\leavevmode\vadjust pre{\hypertarget{ref-6j21xB75}{}}%
Arteaga, C.L., and Engelman, J.A. (2014). ERBB receptors: from oncogene discovery to basic science to mechanism-based cancer therapeutics. Cancer Cell \emph{25}, 282--303. \url{https://doi.org/10.1016/j.ccr.2014.02.025}.

@@

\leavevmode\vadjust pre{\hypertarget{ref-18dmdoj17}{}}%
Bertwistle, D., Zindy, F., Sherr, C.J., and Roussel, M.F. (2004). Monoclonal antibodies to the mouse p19(Arf) tumor suppressor protein. Hybrid Hybridomics \emph{23}, 293--300. \url{https://doi.org/10.1089/hyb.2004.23.293}.

\leavevmode\vadjust pre{\hypertarget{ref-1AV7mz5Fc}{}}%
Bhattacharya, S., and Workman, J.L. (2020). Regulation of SETD2 stability is important for the fidelity of H3K36me3 deposition. Epigenetics Chromatin \emph{13}, 40. \url{https://doi.org/10.1186/s13072-020-00362-8}.

\leavevmode\vadjust pre{\hypertarget{ref-ju5z9qDz}{}}%
Bouaoun, L., Sonkin, D., Ardin, M., Hollstein, M., Byrnes, G., Zavadil, J., and Olivier, M. (2016). TP53 Variations in Human Cancers: New Lessons from the IARC TP53 Database and Genomics Data. Hum Mutat \emph{37}, 865--876. \url{https://doi.org/10.1002/humu.23035}.

\leavevmode\vadjust pre{\hypertarget{ref-GiCMgc6K}{}}%
Bougeard, G., Sesboüé, R., Baert-Desurmont, S., Vasseur, S., Martin, C., Tinat, J., Brugières, L., Chompret, A., de Paillerets, B.B., Stoppa-Lyonnet, D., et al. (2008). Molecular basis of the Li-Fraumeni syndrome: an update from the French LFS families. J Med Genet \emph{45}, 535--538. \url{https://doi.org/10.1136/jmg.2008.057570}.

\leavevmode\vadjust pre{\hypertarget{ref-KlPsMirp}{}}%
Boutelle, A.M., and Attardi, L.D. (2021). p53 and Tumor Suppression: It Takes a Network. Trends Cell Biol \emph{31}, 298--310. \url{https://doi.org/10.1016/j.tcb.2020.12.011}.

\leavevmode\vadjust pre{\hypertarget{ref-Ph0Z7rTW}{}}%
Cerami, E., Gao, J., Dogrusoz, U., Gross, B.E., Sumer, S.O., Aksoy, B.A., Jacobsen, A., Byrne, C.J., Heuer, M.L., Larsson, E., et al. (2012). The cBio cancer genomics portal: an open platform for exploring multidimensional cancer genomics data. Cancer Discov \emph{2}, 401--404. \url{https://doi.org/10.1158/2159-8290.cd-12-0095}.

\leavevmode\vadjust pre{\hypertarget{ref-1EwtuJJw6}{}}%
Chiou, S.-H., Winters, I.P., Wang, J., Naranjo, S., Dudgeon, C., Tamburini, F.B., Brady, J.J., Yang, D., Grüner, B.M., Chuang, C.-H., et al. (2015). Pancreatic cancer modeling using retrograde viral vector delivery and in vivo CRISPR/Cas9-mediated somatic genome editing. Genes Dev \emph{29}, 1576--1585. \url{https://doi.org/10.1101/gad.264861.115}.

\leavevmode\vadjust pre{\hypertarget{ref-G5wVcRrJ}{}}%
Christophorou, M.A., Ringshausen, I., Finch, A.J., Swigart, L.B., and Evan, G.I. (2006). The pathological response to DNA damage does not contribute to p53-mediated tumour suppression. Nature \emph{443}, 214--217. \url{https://doi.org/10.1038/nature05077}.

\leavevmode\vadjust pre{\hypertarget{ref-OK8s0ke5}{}}%
Cicchini, M., Buza, E.L., Sagal, K.M., Gudiel, A.A., Durham, A.C., and Feldser, D.M. (2017). Context-Dependent Effects of Amplified MAPK Signaling during Lung Adenocarcinoma Initiation and Progression. Cell Rep \emph{18}, 1958--1969. \url{https://doi.org/10.1016/j.celrep.2017.01.069}.
